\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2019-06-02 paper/sp.tex
thank referee

For an example of how the model might be interpreted, we can look at
the photometric part of the linear model and see if the combination of
photometry does indeed look like a dust-corrected absolute magnitude,
as we expected (see \sectionname~\ref{sec:data}).
It does! Indeed the model automatically finds a photometric
combination that includes a term close to $H-W2$, which is known as a
good extinction estimator.
And we find that on the two-fold A/B split, the photometric model is extremely stable.
As for the spectroscopic-pixel part of the model, we find that interpretation is
less simple, for two reasons:
One is that the number of pixels is enormous, so the model has huge flexibility.
Another is that although the two splits, A and B, both give similar-performing
models, they have (in detail) different linear coefficients in the spectral space.
That is, the model is not as stable in the spectroscopic domain as it is in the
photometric domain.
This is a generic feature of high-capacity machine-learning methods.
And it means that we did not obtrain as much insight from the spectroscopic model
as we had hoped up-front.

@@

\acknowledgements
It is a pleasure to thank
  Coryn Bailer-Jones (\acronym{MPIA}),
  Sven Buder (\acronym{MPIA}),
  Andy L. Jones,
  Daniel Michalik (\acronym{ESTEC}),
  Melissa Ness (Columbia),
  Joel Zinn (OSU),
  and the participants in the \acronym{MPIA} Milky Way Group Meeting
  and the \apogee\ Science Telecon,
for help with this project.
This project was developed in part at the
2018 \acronym{NYC} Gaia Sprint, hosted by the Center for Computational Astrophysics of
the Flatiron Institute in New York City in 2018 June.

>>>>

For an example of how the model might be interpreted, we can look at
the photometric part of the linear model and see if the combination of
photometry does indeed look like a dust-corrected absolute magnitude,
as we expected (see \sectionname~\ref{sec:data}).
It does! Indeed the model automatically finds a photometric
combination that includes a term close to $H-W_2$, which is known as a
good extinction estimator.
And we find that on the two-fold A/B split, the photometric model is extremely stable.
As for the spectroscopic-pixel part of the model, we find that interpretation is
less simple, for two reasons:
One is that the number of pixels is enormous, so the model has huge flexibility.
Another is that although the two splits, A and B, both give similar-performing
models, they have (in detail) different linear coefficients in the spectral space.
That is, the model is not as stable in the spectroscopic domain as it is in the
photometric domain.
This is a generic feature of high-capacity machine-learning methods.
And it means that we did not obtrain as much insight from the spectroscopic model
as we had hoped up-front.

@@

\acknowledgements
It is a pleasure to thank
  Coryn Bailer-Jones (\acronym{MPIA}),
  Sven Buder (\acronym{MPIA}),
  Andy L. Jones,
  Daniel Michalik (\acronym{ESTEC}),
  Melissa Ness (Columbia),
  Joel Zinn (OSU),
  and the participants in the \acronym{MPIA} Milky Way Group Meeting
  and the \apogee\ Science Telecon,
for help with this project.
The final version of this paper benefitted substantially from the comments
  from the anonymous referee.
This project was developed in part at the
2018 \acronym{NYC} Gaia Sprint, hosted by the Center for Computational Astrophysics of
the Flatiron Institute in New York City in 2018 June.
